\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-03 metatheory-condensed.tex
Fix subscript.

>>>>

  \begin{lstlisting}
  Family STLC_bool extends STLC.

   FInductive ty += ty_bool
   FInductive tm += tm_true ..

   FRecursion subst
     (* Inherits all others *)

     Case tm_true ...

   End subst

   Inherit t1

  i[@₀@] = inh-id : Inh ⋅ {} {} 
  i[@₁@] = inh-ov i[@₀@] (W [@τ₁@]') : Inh ⋅ {ty : 𝕊(W τ₁)} {ty : 𝕊(W τ₁')}
  s[@₂@]' : {ty : 𝕊(W τ₁')} | [ty : 𝕌] 
  i[@₂@] = inh-ov i₁ (W τ₂') 
     : Inh ⋅ {ty : 𝕊(W τ₁); tm : 𝕊(W τ₂)} {ty : 𝕊(W τ₁'); tm : 𝕊(W τ₂') }
  (* recall s[@₃₁@] : {ty : 𝕊(W τ₁); tm : 𝕊(W τ₂)} 
                | [ty : 𝕌;  ..] *)
  s[@₃₁@]' : {ty : 𝕊(W τ₁'); tm : 𝕊(W τ₂')} | [ty : 𝕌; ..; tm_true : tm; ..]
  ↑s[@₃@] : Tm (⋅, [ty : 𝕌; ..; tm_true : tm; ..]) [ty : 𝕌; ..] 
  (* ↑s[@₃@] map (the type of) s[@₃₁@]' to the sealing before inheritance s[@₃₁@] *)
  ii[@₃₀₀@] = inh-id 
           ⫶ Inh ( ⋅, [ty : 𝕌; ..; tm_true : tm; ..])
              (RecSig τ₂  tm)[p[@₀@], ↑s[@₃@]]
              (RecSig τ₂  tm)[p[@₀@], ↑s[@₃@]]
  ii[@₃₀₁@] = inh-extend (inh-extend ii[@₃₀₀@] {p[@₁@]} .. ) {p[@₁@]} ..
        : Inh ( ⋅, [ty : 𝕌; tm :𝕌; ..; tm_true : tm; ..]) 
              (RecSig τ₂  tm)[p[@₀@], ↑s[@₃@]] (RecSig τ₂'  tm)
  i[@₃₁@] = inh+inh i[@₂@] ↑s[@₃@] ii[@₃₀₁@] : 
      Inh ⋅ {ty : 𝕊(W τ₁); ..; subst' : 𝕃(RecSig τ₂ tm)} 
            {ty : 𝕊(W τ₁'); ..; subst' : 𝕃(RecSig τ₂' tm)}
  s[@₃@]' : {ty : 𝕊(W τ₁'); tm : 𝕊(W τ₂'); subst' : 𝕃(RecSig τ₂' tm) }
      | [ty : 𝕌; .. ; tm : 𝕊(W τ₂'); subst' : 𝕃(RecSig τ₂' tm)] 
  i[@₃@] = inh-ov i[@₃₁@] ..
     : Inh ⋅ {ty : 𝕊(W τ₁); tm : 𝕊(W τ₂); subst' : 𝕃(RecSig τ₂ tm); subst : tm → nat → tm → tm}  
             {ty : 𝕊(W τ₁'); tm : 𝕊(W τ₂'); subst' : 𝕃(RecSig τ₂' tm); subst : subst : tm → nat → tm → tm}
  (* recall s₄ : {ty : 𝕊(W τ₁); .. subst : .. } 
      | [ty : 𝕌; .. ; tm : 𝕌; .. ;subst' : 𝕃(RecSig τ₂ tm); subst : ..] *)
  s[@₄@]' : {ty : 𝕊(W τ₁'); .. subst : .. } 
        | [ty : 𝕌; .. ; tm : 𝕌; .. ;subst' : 𝕃(RecSig τ₂ tm); subst : ..]
  ↑s[@₄@] : Tm (⋅, [ty : 𝕌; .. ; tm : 𝕌; .. ; subst' : 𝕃(RecSig τ₂ tm);subst : ..]) 
          [ty : 𝕌; .. ; tm : 𝕌; .. ;subst' : 𝕃(RecSig τ₂ tm); subst : ..]
  i[@₄@] = inh-inh i[@₃@] ↑s[@₄@] 
         : Inh ⋅ {ty : 𝕊(W τ₁); .. subst : ..; t1 : 𝕊(tm_var 0)} 
                 {ty : 𝕊(W τ₁'); .. subst : ..; t1 : 𝕊(tm_var 0)} 
  \end{lstlisting}

  \end{multicols}
  \end{minipage}
  \caption{Inheritance Metatheory}\label{fig:inheritance}
  \end{figure}
